Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2022-07-22 Paper/Manuscript_Stats&Comp/reply_letter_2nd_STCO.tex
More edits to the paper and response letter 2

We apologize for creating confusion with our notation here. We work with a normalized lengthscale, i.e., a lengthscale $\ell$ relative to the half-range ($S$) of the input domain ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. We have now clarified the notation by using different symbols for lengthscale and normalized lengthscale throughout the paper.

%added an additional paragraph to make it more clear in the second-to-last paragraph in Section 4.3.1.

>>>>

We apologize for creating confusion with our notation here. {\color{blue}The diagnostic Figure 5 and equations (19-24) work with a normalized lengthscale, i.e., a lengthscale $\ell$ normalized by the zero-mean, symmetric interval $S$ which contains the inpus values $x_i$ ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. In concrete in step A.1 in Section 4.5.1 we recommend values for a first guess of the lengthscale based on the normalized lengthscale. We have now clarified the role and use of the normalized lengthscale relative to $S$ throughout the paper.}

%We work with a normalized lengthscale, i.e., a lengthscale $\ell$ relative to the half-range ($S$) of the input domain ($\ell/S$), so the conclusions can be easily referred to any specific scale of the input domain. We have now clarified the notation by using different symbols for lengthscale and normalized lengthscale throughout the paper.
